---
title: "Data exploration Toronto renting regulations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## *Data retrieval*

We retrieved our data from the following [website](http://insideairbnb.com/get-the-data.html). The goal of our research is to figure out whether the implemented renting market regulations have an effect on the rental prices on AirBnB in Toronto. In case this has a negative effect, then this regulation could also be suggested for other cities facing similar problems as Toronto did.

The website provides data files with a lot of information on AirBnB in Toronto per month for the time period of a year. In order to inspect the effect of the regulation, we retrieved two data files:
  1. Information on listings in Toronto of August 2020
  2. Information on listings in Toronto of August 2021

## Data merging

We want to compare the information on listings prior to the regulations and after the regulations. Therefore, it is important to merge to two data files that we retrieved before we do any data preparation. The variable "regulation" is created as a dummy variable for this first. After that, we can merge the two data sets into a data set that we can use to further prepare the data for analysis.

## Data exploration

In order to understand the research, it is important to be well informed about the variables in the data. The data consists out of 75 variables which give different information on the AirBnB listings in Toronto. Multiple variables are used in our analysis. There is more information given about the variables used in our research below. Most information is retrieved from the Inside AirBnB Data dictionary which is given on the previously named website.

### Variables used for main research

#### Regulation

The created dummy variable "Regulation" indicates whether the information about the listing comes from prior to the regulation or after the regulation. The value 0 indicates the moment prior to the regulation (August, 2020), while the value 1 indicates the moment after the regulation (August, 2021).

#### Price

The variable "price" reflects the daily price in local currency.

### Control variables

In order to increase the accuracy of our research, we added several covariates to our research.

#### room_type

All homes are grouped into the following four room types:
  1. entire home/apt
  2. hotel room
  3. shared room
  4. private room

```{r, echo= FALSE, results='hide', message= FALSE, warning=FALSE}
# Load Libraries
library(googledrive)
library(readr)

dir.create('../../data')

#listings august 2020
data_id <- "1f3L-KHmC89xcn7LIMpGsfwh8zMu8orPE"
out_file <- "../../data/listings0820.csv"

drive_download(
    as_id(data_id), 
    path = out_file, 
    overwrite = TRUE)

#listings august 2021
data_id2 <- "11Xy7UtyZaYsOfU4xIDeLA_syv1WFeDV4"
out_file2 <- "../../data/listings0821.csv"

drive_download(
    as_id(data_id2), 
    path = out_file2, 
    overwrite = TRUE)

# Load Data
listings0820 <- read.csv("../../data/listings0820.csv")
listings0821 <- read.csv("../../data/listings0821.csv")

#Create dummy variable 'regulation' in both datasets. 
# Dummy variable = 0 for dataset before regulation
# Dummy variable = 1 for dataset after regulation

listings0820$regulation <- 0
listings0821$regulation <- 1

#Merge datasets together to be able to perform analysis
listings_merged <- merge(listings0820, listings0821, all.x=TRUE, all.y=TRUE)

# Write output
dir.create('../../gen')
dir.create('../../gen/data-preparation')
dir.create('../../gen/data-preparation/input')
write.csv(listings_merged, "../../gen/data-preparation/input/merged_data.csv", row.names = FALSE)

# Load the data
all_data <- read.csv(file = '../../gen/data-preparation/input/merged_data.csv')

# Create bar plot
counts <- table(all_data$room_type)
counts

barplot(counts, main="Room type",
        col = c("cadetblue3", "cadetblue1","coral3", "coral1" ),
        xlab = "Room type",
        ylab = "Number of objects",
        legend = c("Entire home/apt", "Hotel room", "Private room", "Shared room"),
        args.legend = list(title = "Room type", x = "topright",
                           cex = .7)  ) 
```

#### neighbourhood_cleansed

The neighbourhood as geocoded using the latitude and longitude against neighborhoods as defined by open or public digital shape files. There are too many objects in this variable, so we will not create a plot for this.

#### host_since

The variable host_since reflects the date the host/user was created. For hosts that are Airbnb guests this could be the date they registered as a guest. The line plot below shows the number of new hosts per year which were listed in August 2021.

```{r, echo= FALSE, results='hide', message= FALSE, warning=FALSE}
# Load libraries
library(dplyr)
library(tibble)
library(ggplot2)
library(lubridate)

# Create new data file as a table for dates
dm <- read.table(text = listings0821$host_since, header = FALSE)

dm$V1 <- ymd(dm$V1)

dm$V2 <- as.Date(dm$V1, "%m/%d/%Y")
dm$V2 <- format(dm$V2, "%Y")

# Create a newe data frame from the table
df_table <- as.data.frame(table(dm$V2))

# Transform V1 into a numeric
df_table$Var1 <- as.numeric(levels(df_table$Var1))[df_table$Var1] 

# Plot
ggplot(df_table, aes(x=Var1, y=Freq)) +
  geom_line( color="steelblue") + 
  geom_point() +
  xlab("Year") +
  ylab("Number of hosts") +
  ggtitle("Number of hosts per year") +
  scale_x_continuous(breaks = df_table$Var1) +
  theme_minimal() +
  theme(axis.text.x=element_text(angle=60, hjust=1))
```

#### host_is_superhost

This variable shows whether the host of a listing has the superhost status. These are experienced hosts who are an example host for other hosts. The values of this variable show either t (= true) or f (= false).

```{r, echo= FALSE, results='hide', message= FALSE, warning=FALSE}
# Load the data
all_data <- read.csv(file = '../../gen/data-preparation/input/merged_data.csv')

# Create barplot
counts <- table(all_data$host_is_superhost)
counts
counts <- counts[-1] 

barplot(counts, main="Host is superhost",
        col = c(border="#69b3a2", col="white"),
        xlab = "True or False",
        ylab = "Number of objects",
        legend = c("False", "True"),
        args.legend = list(title = "Host is superhost", x = "topright",
                           cex = .7))
```

#### host_identity_verified

This variable shows whether the host of a listing is officially indentified. The values of this variable show either t (= true) or f (= false).

```{r, echo= FALSE, results='hide', message= FALSE, warning=FALSE}
# Load the data
all_data <- read.csv(file = '../../gen/data-preparation/input/merged_data.csv')

# Create barplot
counts <- table(all_data$host_is_superhost)
counts
counts <- counts[-1] 

barplot(counts, main="The identity of host verified",
        col = c(border="#69b3a2", col="white"),
        xlab = "True or False",
        ylab = "Number of objects",
        legend = c("False", "True"),
        args.legend = list(title = "The identity of host verified", x = "topright",
                           cex = .7))
```

